---
title: "introduction"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(classquiz)
```

# Why

Small quizes in lectures can help gauge how well the students have understood the material.

Commercial services exist, for example ###, but these need a licence and don't integrate nicely into a presentation made with quarto or rmarkdown.

`classquiz` is designed to google forms to ask the questions, google sheets to store the responses, but other services could be substituted.
`classquiz` uses observable to download the results from google sheets, process and plot them in the lecture slides.

# Procedure

1) Make and publish google form.
 - single question (type?) per form. IE make several small forms rather than one huge one.
2) Have google form save results in google sheets
3) Share read access to google sheet with anyone who has link
4) Add question form to quarto with `cq_add_form()`. 
This function displays the URL provided in an iframe.

```{r}
#| echo: fenced
cq_add_form(
  form_url = "https://docs.google.com/forms/d/e/1FAIpQLSeLIUnzdTfBUqjr_X0MvF7JBDQgy_mndeZVsjgW4JR3tFRHSw/viewform?usp=sharing&ouid=107915462972182704713"
)
```


5) Add the results of the quiz to quarto with `cq_add_results()`. 
This function makes a set of observable code chunks that download the data, process it and plot it.
You must use the `#| output: asis` code block option so that the generated observable chunks are correctly interpreted.
```{r}
#| echo: fenced
#| output: asis
#cq_add_results()
```

